\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-19 paper.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
%\usepackage{bm}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    \notaL{El punto del electrodo hazlo más chico que el ancho
      del cable.} with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
and $\phi$ the electric potential. For a
stationary situation
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $6.2\text{mm}\times2.03\text{cm}$) with an uncovered sample area
of about $1.21\text{cm}^2$. The height of the liquid was set at
$c=1\text{cm}$. The cathode was a
platinum wire that with a diameter of $0.41\text{mm}$ insulated by a
teflon cylinder of external diameter $2\text{mm}$. \notaL{¿Están
  bien estos diámetros?} with an uncovered tip located at $\bm r_0=(x_0,
y_0,z_0)=(0.1,0.31,0.9)$.
We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$, which required an attack time of
$t_1=600 \text{s}$ and other samples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$ and $t_2=200 \text{s}$ . \notaC{
Coloque los tiempo de ataque para $t_1$ y $t_2$}
\subsection{Morphological studies}
\label{sec:morph-stud}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}). \notaL{¿Sí se midió la porosidad con SEM?}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    \notaL{El punto del electrodo hazlo más chico que el ancho
      del cable.} with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
and $\phi$ the electric potential. For a
stationary situation
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \phi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $6.2\text{mm}\times2.03\text{cm}$) with an uncovered sample area
of about $1.21\text{cm}^2$. The height of the liquid was set at
$c=1\text{cm}$. The cathode was a
platinum wire that with a diameter of $0.41\text{mm}$ insulated by a
teflon cylinder of external diameter $2\text{mm}$. \notaL{¿Están
  bien estos diámetros?} with an uncovered tip located at $\bm r_0=(x_0,
y_0,z_0)=(0.1,0.31,0.9)$.
We manufactured a sample applying a current $I=5\text{mA}$,
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$,\notaL{verificar} during an attack time
$t_1=600 \text{s}$, and another sample using a larger
current $I=40\text{mA}$, corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$, for a time $t_2=200 \text{s}$ . \notaC{
Coloque los tiempo de ataque para $t_1$ y $t_2$}
\subsection{Morphological studies}
\label{sec:morph-stud}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}). \notaL{¿Sí se midió la porosidad con SEM?}
